### 2023-03-29 resilience-safe-up.tex
up

\begin{corollary}\label{B-up-up}
The bounded resilience problem is decidable for WSTS with effective pred-basis,
strong compatibility
 $\Safe=\uparrow \Safe$
and $\Bad=\uparrow \Bad$.
\end{corollary}

>>>>

\begin{corollary}\label{B-up-up}
The bounded resilience problem is decidable for WSTS with effective pred-basis,
strong compatibility
 $\Safe=\uparrow \Safe$
and $\Bad=\uparrow \Bad \setminus \Safe$.
\end{corollary}
